\sysfull

### 2017-11-15 paper/paging.tex
review of paging section (second pass)

@@

\sys paging scheme partitions the non-volatile memory address space into pages of {\em protected data}. As they are accessed by a task, pages of protected data are swapped into a {\em page buffer} \texttt{pagesBuf} that is stored in volatile memory and holds a pre-determined number of pages. When any modified page in the page buffer is swapped out, it is buffered in a dedicated {\em commit buffer} \texttt{pagesTemp} for later. \sys uses two-phase commit to write buffered, modified pages back to their original memory locations atomically, ensuring data consistency even with power failures. \sys's page-based memory model allows moving large blocks of data between non-volatile and volatile memory, which \sys does efficiently using common,
hardware DMA block-copy operations, unlike prior work~\cite{chain,alpaca} that moves one variable at a time. Moreover, \sys's paging and buffering scheme is a key enabler of task coalescing, which we describe in Section~\ref{sec:task_coalescing}. Paging simplifies coalescing because deferring a commit of paged data at a task boundary entails leaving paged data buffered only, not requiring additional state management logic at task boundaries.

@@

\sys virtualizes the protected, non-volatile data that a task can access through a modified memory interface. The interface includes two operations: \texttt{RVAR(var)}, which reads the value of the memory location {\tt var} and \texttt{WVAR(var,val)}, which writes the value {\tt val} into the memory location {\tt var}. {\tt RVAR} and {\tt WVAR} operations translate a variable's physical address in non-volatile memory and translates it into a \emph{virtual address} in the page buffer in volatile memory.  In \sys, a virtual address is composed of a \emph{page tag} and a \emph{page offset}. The page tag identifies in which page of non-volatile memory the memory location resides and the page offset identifies a particular byte of that page.

>>>>

\sys's paging and buffering scheme is a key enabler of task coalescing, which we described in Section~\ref{sec:task_coalescing}. Paging simplifies coalescing because deferring a commit of paged data at a task boundary entails leaving paged data buffered only, not requiring additional state management logic at task boundaries.

@@

\sys paging scheme partitions the non-volatile memory address space into pages of {\em protected data}. As they are accessed by a task, pages of protected data are swapped into a {\em page buffer} \texttt{pagesBuf} that is stored in volatile memory and holds a pre-determined number of pages. When any modified page in the page buffer is swapped out, it is buffered in a dedicated {\em commit buffer} \texttt{pagesTemp} for later. \sys uses two-phase commit to write buffered, modified pages back to their original memory locations atomically, ensuring data consistency even with power failures. \sys's page-based memory model allows moving large blocks of data between non-volatile and volatile memory, which \sys does efficiently using common, hardware DMA block-copy operations, unlike prior work~\cite{chain,alpaca} that moves one variable at a time.

@@

\sys virtualizes the protected, non-volatile data that a task can access through a modified memory interface. The interface includes two operations (Table~\ref{tab:viper_syntax}): \texttt{RVAR(var)}, which reads the value of the memory location {\tt var} and \texttt{WVAR(var,val)}, which writes the value {\tt val} into the memory location {\tt var}. {\tt RVAR} and {\tt WVAR} operations translate a variable's physical address in non-volatile memory and translates it into a \emph{virtual address} in the page buffer in volatile memory.  In \sys, a virtual address is composed of a \emph{page tag} and a \emph{page offset}. The page tag identifies in which page of non-volatile memory the memory location resides and the page offset identifies a particular byte of that page.
